CONEM2024-0025\\ ABC MULTICRITERIA CLASSIFICATION WITH ANALYTICAL HIERARCHY PROCESS: HOW TO FORCE CONSISTENCY OF PAIRWISE COMPARISONS MATRIX

### 2024-02-05 accepted/CONEM2024/FCPCOM/CONEM2024.tex
new beautiful multicriteria method - I belive it will work

	The solution that we adopted in this work for multicriteria classification with lead time and billing criteria, was based on the work of Willians. A single measure was adopted for these two criteria (lead time billing) dividing the billing by the lead time.

@@

\begin{equation}
	\label{eq:weight}
	\rho_{p} = (wb + wlt) * \frac{b_p}{lt_p} + \sum_{q=1}^{\textrm{NQ}}{w_{\sigma_q}*\frac{b_{e_{p\sigma_q}}}{lt_{e_{p\sigma_q}}}} + \sum_{b=1}^{\textrm{NB}}{w_{\beta_b}*w_{p\beta_b}}, \quad p= 1,...,\textrm{NP}
\end{equation}

@@

$\frac{b_p}{lt_p}$ is the lead time billing of product $p$;

>>>>

	The solution that we adopted in this work for multicriteria classification with lead time and billing criteria, was inspired on the work of Willians. A single measure was adopted for these two criteria (lead time billing) dividing the billing by the complement of the lead time percentage.

@@

\begin{equation}
	\label{eq:weight}
	\rho_{p} = (wb + wlt) * \frac{b_p}{1 + (lt^{\max} - lt_p)} + \sum_{q=1}^{\textrm{NQ}}{w_{\sigma_q}*\frac{b_{e_{p\sigma_q}}}{1 + (lt^{\max} - lt_{e_{p\sigma_q}})}} + \sum_{b=1}^{\textrm{NB}}{w_{\beta_b}*w_{p\beta_b}}, \quad p= 1,...,\textrm{NP}
\end{equation}

@@

$\frac{b_p}{1 + (lt^{\max} - lt_p)}$ is the lead time billing of product $p$;
